Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-09-19 paper/aaaiFormat.tex
abstract 2

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novelty transfer learning method \textsc{LTDetector} to deal with the task.  
1) \textsc{LTDetector} bases on the following fact, that microblog is short but it can be enriched by knowledge base semantically.
Knowledge base can be a good supplementary for event detection on microblog stream.
But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
We propose a lightweight transfer learning method \textsc{LTDetector} for high accurate event detection.  
In this proposed method, 1) the data structure \textit{history states} can be extracted from knowledge base to restore what happened; 2) \textit{recent states} are updated by \textit{history states} and upcoming text streams via our proposed probabilistic model HS-Prior-LDA to maintain what is happening; 3) events can be detected based on recent states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{LTDetector}.
\textsc{LTDetector} promotes the accuracy rate by 9\% without  sacrificing the recall rate.

>>>>

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level.
The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noisy accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
